---
title: "BR09_02.Reannotation of peptides"
author: "Robert Warneford-Thomsom"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document:
    toc: true
    toc_float: true
    number_sections: true
    theme: flatly
editor_options: 
  chunk_output_type: console
knit: (function(inputFile, encoding) { 
      out_dir <- file.path(dirname(dirname(inputFile)), "Reports");
      if (!dir.exists(out_dir)) dir.create(out_dir);
      rmarkdown::render(inputFile,
                        encoding=encoding, 
                        output_file=file.path(out_dir,
                        paste0(tools::file_path_sans_ext(basename(inputFile)), ".html")))
                        })
   #directs html output to 'Reports' folder in parent directory of markdown file
---

Knitted on: `r Sys.time()`

# Setup

## Global options + wd

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
homedir <- "/home/rwt"
Experiment = "BR09.2021.Young.TF.RBRID"
wd <- paste0(homedir,"/analyses/2021/", Experiment)
anno.dir <- file.path(wd, "Annotation_Files")

evalFlag = F # option to evaluate all chunks
```

# Libraries

```{r load libs}
pacman::p_load(furrr,
               purrr,
               tidyverse,
               tictoc,
               Biostrings,
               xlsxjars,
               xlsx,
               VennDiagram,
               gridExtra,
               future.apply,
               ggpubr,
               ggExtra,
               gtable)

```

## Functions

### RBR-ID functions (RWT)

```{r functions}
source("/home/rwt/scripts/R/RBRID_functions.R",
       local = knitr::knit_global(),
       print.eval = T,
       max.deparse.length = 10000)
```

### setupCluster
```{r setupCluster}
setupCluster <- function(filenumber, total_cores)
  #function to set up threads using R packages Future
  #sets up nested parallel environment where total threads are divided between number of desired threads
  # can provide either integer number of files or simply list to be processed
{
  main_threads = ifelse(is.list(filenumber),length(filenumber),filenumber)
  sub_threads <- floor(total_cores / main_threads)

  #specify nested parallel threads to allow nested parallel computations
  #total threads equals length(run_index) * subthreads)
  future::plan(list(future::tweak(multisession, workers = main_threads),
            future::tweak(multisession, workers = sub_threads)))
}
```
### my_rename

```{r my_rename}
#function that allows renaming list elements similarly to dplyr::rename syntax
my_rename <- function(.x, ..., .strict = TRUE) {
  pos <- tidyselect::eval_rename(quote(c(...)), .x, strict = .strict)
  names(.x)[pos] <- names(pos)
  .x
}
```

# RB tables

## Load 220316 Tables from Roberto

```{r RB_tables}
rb_mESC <- read_delim(file.path(wd, "raw_data/220316.rbrid.mESCs_2016.interpro.tsv"),
          delim = "\t")

rb_K562 <- read_delim(file.path(wd, "raw_data/220316.rbrid.K562.interpro.tsv"),
          delim = "\t")

old_K562_TFs <- rb_K562 %>% 
  filter(peptides_detected > 2 & !is.na(whitehead_TF) & whitehead_TF != "") %>%
  pull(whitehead_TF)  %>% 
  unique()

peplist <- readRDS(file.path(wd, "rds", "BR09_02_anno.IPR.wh.quant.rds"))

new_K562_TFs <- peplist$K562 %>% 
  filter(peptides_detected > 2 & !is.na(whitehead_TF) & whitehead_TF != "") %>%
  pull(whitehead_TF)  %>% 
  unique()

new_K562_TFs[!new_K562_TFs %in% old_K562_TFs]
old_K562_TFs[!old_K562_TFs %in% new_K562_TFs]

```

## Files for Fig1 previous analysis DBD overlap

```{r DBD_overlap}
#peptides into list
rbpeps <- list(mESC = rb_mESC,
               K562 = rb_K562)

# Load Interpro DBD table
Interpro_DBD.table <- read.xlsx2(
  file.path(anno.dir, "220309 DBD Interpro table.xlsx"),
  sheetIndex = 1)

rbpeps <- lapply(rbpeps, function(rbrid){
  
  #annotate TF peptides that overlap Interpro DBDs
  #initialize column as 0, but set "none in protein" for proteins lacking any known IPR DBD
  rbrid$interpro_DBD <- lapply(Interpro_DBD.table$IPR_ID,
                     function(IPR) {
                       dbd <- Interpro_DBD.table %>%
                         filter(IPR_ID == IPR) %>% 
                         pull(Name) %>%
                         unlist()
                       out <- rep("", nrow(rbrid))
                       index_match <- grepl(IPR,
                                            rbrid$interpro_peptide)
                       
                       out[index_match] <- paste(dbd, " ")
                       return(out)
                                }) %>%
    do.call("paste0", .) %>%
    gsub("\ *$", "", x=.) # add spacer between results
  
  return(rbrid)
})
rbrid <- rbpeps$K562
dataset <- "K562"


plots <- imap(rbpeps, function(rbrid, dataset) {
  
   # extract species information from dataset name
 if (grepl("K562|HCT116|HepG2", dataset)) {
    species = "human"
  } else if (grepl("mESC", dataset)) {
    species = "mouse"
  }
  trim_name <- gsub(x = dataset, pattern = "_.*", "")
  
  
  #annotate RBR hits
  if (species == "mouse") {
    rbrid$strict <- rbrid$pval < 0.05 & rbrid$logFold < 0
  } else {
    rbrid$strict <- rbrid$padj < 0.05 & rbrid$logFold < 0
  }
  
   #Filter for whitehead TF peptides
  df <- rbrid %>% 
    filter(!is.na(whitehead_TF)) %>%
    filter(peptides_detected > 2) %>% # filter for peptides from proteins with at least 3 peptides
    filter(strict)  
  
  

  Domain.overlaps <- df %>% 
    filter(strict) %>% 
    group_by(symbol) %>%
    summarise(
      interpro.overlaps = paste0(interpro_DBD, collapse = "|") %>%
                                      str_split(. , pattern = "\\|") %>%
                                      unlist() %>%
                                      .[. != ""] %>%
                                      length()
    ) %>% 
    ungroup()
  
  #label DBD overlaps > 2 "3 or more"
  Domain.overlaps$interpro.overlaps[Domain.overlaps$interpro.overlaps > 2] <- "3 or more"
  
  #for symbols that do not contain any IPR DBD, label as none in protein
  interpro_dbd <- paste0(Interpro_DBD.table$IPR_ID, collapse = "|")
  
  none_index <- sapply(Domain.overlaps$symbol, function(symbol) {
    interpro <- df$interpro_protein[df$symbol == symbol] %>%
      paste0(.,collapse = "|") %>%
      str_split(. , pattern = "\\|") %>%
      unlist() %>%
      unique() %>%
      paste0(.,collapse = "|")
    
    !grepl(interpro_dbd, interpro)
    }) %>% which()

  
  Domain.overlaps$interpro.overlaps[none_index] <- "no annotated DBD"
  
  # order factor
  Domain.overlaps$interpro.overlaps <- factor(Domain.overlaps$interpro.overlaps) %>%
    fct_relevel(., c("no annotated DBD", "0", "1", "2", "3 or more"))
  
  Domain.overlaps <- Domain.overlaps %>%
    arrange(interpro.overlaps)
  

y <- ggplot(Domain.overlaps, aes(y="count", fill=interpro.overlaps)) +
  geom_bar() +
  theme_bw() + 
  ylab("") +
  xlab("number of proteins") +
  ggtitle(paste0(trim_name, " RBR-ID hit overlap with Interpro DNA-binding Domains\nTF protein hits: ", nrow(Domain.overlaps))) +
  coord_flip() +
  scale_fill_manual("number of peptide overlaps", 
                    values = c("no annotated DBD" = "dodgerblue2",
                               "0" = "grey",
                               "1" = "grey44",
                               "2" = "black",
                               "3 or more" = "orange")) +
  theme(axis.text.x=element_blank(),
        text = element_text(size=10),
        axis.ticks.x = element_blank())
return(y)
})

```

### Fig 1
```{r Fig1}
pdf(file.path(wd, "figures", "BR09_08_Fig1_RB_tables_DBD_overlap.pdf"))
p1 <- ggarrange(plotlist = plots, ncol = 1)
p1
dev.off()
```

### Files for Fig 1.2 (outside DBD)
```{r prep1.2}
rbrid <- rbpeps$K562
dataset <- "K562"

plots <- imap(rbpeps, function(rbrid, dataset) {
  
   # extract species information from dataset name
 if (grepl("K562|HCT116|HepG2", dataset)) {
    species = "human"
  } else if (grepl("mESC", dataset)) {
    species = "mouse"
  }
  trim_name <- gsub(x = dataset, pattern = "_.*", "")
  
  
  #annotate RBR hits
  if (species == "mouse") {
    rbrid$strict <- rbrid$pval < 0.05 & rbrid$logFold < 0
  } else {
    rbrid$strict <- rbrid$padj < 0.05 & rbrid$logFold < 0
  }
  
   #Filter for whitehead TF peptides
  df <- rbrid %>% 
    filter(!is.na(whitehead_TF)) %>%
    filter(peptides_detected > 2) %>% # filter for peptides from proteins with at least 3 peptides
    filter(strict)  
  
  
  #calculate peptides in each protein that do not overlap DBD
  Domain.overlaps <- df %>% 
    filter(strict) %>% 
    group_by(symbol) %>%
    summarise(
      nonDBD = sum(interpro_DBD == "")) %>% 
    ungroup()
  
  #label DBD overlaps 
  Domain.overlaps$nonDBD[Domain.overlaps$nonDBD > 2] <- "3 or more"
  
  #for symbols that do not contain any IPR DBD, label as none in protein
  interpro_dbd <- paste0(Interpro_DBD.table$IPR_ID, collapse = "|")
  
  none_index <- sapply(Domain.overlaps$symbol, function(symbol) {
    interpro <- df$interpro_protein[df$symbol == symbol] %>%
      paste0(.,collapse = "|") %>%
      str_split(. , pattern = "\\|") %>%
      unlist() %>%
      unique() %>%
      paste0(.,collapse = "|")
    
    !grepl(interpro_dbd, interpro)
    }) %>% which()

  
  Domain.overlaps$nonDBD[none_index] <- "no annotated DBD"
  
  # order factor
  Domain.overlaps$nonDBD <- factor(Domain.overlaps$nonDBD) %>%
    fct_relevel(., c("3 or more", "2", "1", "0", "no annotated DBD"))
  
  labels <- levels(Domain.overlaps$nonDBD)
  values = c("3 or more" = "orange",
                               "2" = "black",
                               "1" = "grey44",
                               "0" = "grey",
                               "no annotated DBD" = "dodgerblue2"
                               )
  
  Domain.overlaps <- Domain.overlaps %>%
    arrange(nonDBD)
  

y <- ggplot(Domain.overlaps, aes(y="count", fill=nonDBD)) +
  geom_bar() +
  theme_bw() + 
  ylab("") +
  xlab("number of proteins") +
  ggtitle(paste0(trim_name, " TF non-DBD RBR-ID hits\nTF protein hits: ", nrow(Domain.overlaps))) +
  coord_flip() +
  scale_fill_manual("number of non-DBD peptides",
                    labels = labels,
                    values = values[labels]) +
  theme(axis.text.x=element_blank(),
        text = element_text(size=10),
        axis.ticks.x = element_blank())
return(y)
})
```

### Fig 1.2
```{r Fig1.2}
pdf(file.path(wd, "figures", "BR09_08_Fig1.2_RB_tables_nonDBD_overlap.pdf"))
p1 <- ggarrange(plotlist = plots, ncol = 1)
p1
dev.off()
```

### Files for Fig 1.3 (outside DBD | inside DBD | both)
```{r prep1.3}
rbrid <- rbpeps$K562
dataset <- "K562"

plots <- imap(rbpeps, function(rbrid, dataset) {
 species <- Whatspecies(dataset) 
 trim_name <- gsub(x = dataset, pattern = "_.*", "")
  
  
  #annotate RBR hits
  if (species == "mouse") {
    rbrid$strict <- rbrid$pval < 0.05 & rbrid$logFold < 0
  } else {
    rbrid$strict <- rbrid$padj < 0.05 & rbrid$logFold < 0
  }
  
   #Filter for whitehead TF peptides
  df <- rbrid %>% 
    filter(!is.na(whitehead_TF)) %>%
    filter(peptides_detected > 2) %>% # filter for peptides from proteins with at least 3 peptides
    filter(strict)  
  
  
  #categorize peptides:
  #1) those with hits only within the DBD
  #2) those with only outside the DBD
  #3) those with hits in both
  Domain.overlaps <- df %>% 
    filter(strict) %>% 
    group_by(symbol) %>%
    summarise(
      nonDBD = any(interpro_DBD == ""),
      DBD = any(interpro_DBD != "")) %>%
    ungroup()
  
  #label DBD overlaps
  # categorize proteins into above groups
Domain.overlaps <- Domain.overlaps %>%
    mutate(Domain = case_when(nonDBD & !DBD ~ "All hits outside DBD",
                              !nonDBD & DBD ~ "All hits inside DBD",
                              nonDBD & DBD ~ "hits inside and outside DBD")
    )
  
  #for symbols that do not contain any IPR DBD, label as none in protein
  interpro_dbd <- paste0(Interpro_DBD.table$IPR_ID, collapse = "|")
  
  none_index <- sapply(Domain.overlaps$symbol, function(symbol) {
    interpro <- df$interpro_protein[df$symbol == symbol] %>%
      paste0(.,collapse = "|") %>%
      str_split(. , pattern = "\\|") %>%
      unlist() %>%
      unique() %>%
      paste0(.,collapse = "|")
    
    !grepl(interpro_dbd, interpro)
    }) %>% which()
  
  
  
  Domain.overlaps$Domain[none_index] <- "no annotated DBD"
  
  # order factor
  Domain.overlaps$Domain <- factor(Domain.overlaps$Domain) %>%
    fct_relevel(., c("All hits outside DBD",
                     "hits inside and outside DBD",
                     "All hits inside DBD",
                     "no annotated DBD"))
  
  labels <- levels(Domain.overlaps$Domain)
  cbp1 <- c("#999999", "#E69F00", "#56B4E9", "#009E73",
          "#F0E442", "#0072B2", "#D55E00", "#CC79A7")
  colors <- cbp1
  colors <- colors[1:length(labels)]
  names(colors) <- labels
  
  Domain.overlaps <- Domain.overlaps %>%
    arrange(Domain)
  

y <- ggplot(Domain.overlaps, aes(y="count", fill=Domain)) +
  geom_bar() +
  theme_bw() + 
  ylab("") +
  xlab("number of proteins") +
  ggtitle(paste0(trim_name, " TF non-DBD RBR-ID hits\nTF protein hits: ", nrow(Domain.overlaps))) +
  coord_flip() +
  scale_fill_manual("number of non-DBD peptides",
                    labels = labels,
                    values = colors) +
  theme(axis.text.x=element_blank(),
        text = element_text(size=10),
        axis.ticks.x = element_blank())
return(y)
})
```

### Fig 1.3
```{r Fig1.3}
pdf(file.path(wd, "figures", "BR09_08_Fig1.3_RB_tables_DBD_category.pdf"))
p1 <- ggarrange(plotlist = plots, ncol = 1)
p1
dev.off()
```

# RWT updated analysis

###  Fig 2: TF & RBR overlap (updated analysis)
```{r venn}
run_index <- c("K562_E")

peplist <- readRDS(file.path(wd, "rds", "BR09_11_anno.IPR.wh.prot_rbd.quant.rds"))[run_index]

#duplicate mESC for secondary hits
# names(peplist) <- c("Hela", "Hela_secondary")

venn_plots <- imap(peplist, function(rbrid, dataset) {
  # ignore proteins that don't have at least x peptides
  filt <- rbrid[rbrid$peptides_detected > 2,]  
  
  trim_name <- gsub(x = dataset, pattern = "_.*", "")
  stringency <- "Primary" # primary or secondary hits
  
  FDR = T #set FDR comparison as true
  if (trim_name %in% c("mESC")) {
    FDR = F
  }
  
  cutoff = 0.05
  
  if(grepl("secondary", dataset)){
    cutoff = 0.1 
    stringency <- "Primary and secondary"
  }
  
  if (FDR) {
    filt.hits <- filt %>%
      filter(log2fold < 0 & padj < cutoff)# then find hits
  }
  
  if (dataset == "mESC") {
  filt.hits <- filt %>%
    filter(log2fold < 0 & pval < cutoff)# then find hits
  }

  # Count number of proteins in various groups
  n.prot     <- length(unique(filt$uniprotID))
  n.TFs      <- length(unique(filt$whitehead_TF[filt$whitehead_TF != ""])) 
  n.hits     <- length(unique(filt.hits$uniprotID))
  overlap    <- filt.hits %>%
    filter(whitehead_TF != "") %>%
    pull(symbol) %>%
    unique() %>%
    length()

  # Overlaps
  pval <- phyper(q = overlap-1,
                 m = n.hits,
                 n = n.prot-n.hits,
                 k = n.TFs,
                 lower.tail = F) %>%
    signif(., digits = 3)

  venn <- draw.pairwise.venn(area1 = n.hits,
                     area2 = n.TFs,
                     cross.area = overlap,
                     fill = c("red", "blue"),
                     alpha = c(0.5,0.5),
                     category = c(paste0(stringency, " hits"),
                                  paste0(stringency, " hits TFs (≥3 peptides)")),
                     scaled = T,
                     cex = 1,
                     cat.pos = c(340, 180),
                     cat.dist = c(0.05, 0.1),
                     cat.cex = 1,
                     ind = F)
  
  
  out <- ggarrange(textGrob(paste0("overlap p = ", pval),
                            gp = gpar(col = "black",
                                      fontsize = 15)),
                   venn, 
                   ncol = 1, nrow = 2,heights = c(1,5))

return(out)
})

ggarrange(plotlist = venn_plots[2],
          ncol =1,
          nrow=1)
```

## Fig3 updated DBD overlap

```{r DBD_overlap_fig}
peplist <- readRDS(file.path(wd, "rds", "BR09_11_anno.IPR.wh.prot_rbd.quant.rds"))[run_index]

rbrid <- peplist[[run_index[2]]]
dataset <- run_index[1]

DBD_plots <- imap(peplist, function(rbrid, dataset) {
   # extract species information from dataset name
 
  species <- Whatspecies(dataset)
  trim_name <- gsub(x = dataset, pattern = "_.*", "")
  
  if(trim_name == "Hela"){
    cutoff = 0.1 
  } else {cutoff = 0.05}
  
  #annotate RBR hits
  if (species == "mouse") {
    rbrid$strict <- rbrid$pval < cutoff & rbrid$log2fold < 0
  } else {
    rbrid$strict <- rbrid$padj < cutoff & rbrid$log2fold < 0
  }
  
   #Filter for whitehead TF peptides
  df <- rbrid %>% 
    filter(whitehead_TF != "") %>%
    filter(peptides_detected > 2) %>% # filter for peptides from proteins with at least 3 peptides
    filter(strict)  

  Domain.overlaps <- df %>% 
    group_by(whitehead_TF) %>%
    summarise(interpro.overlaps = sum(interpro_DBD != ""),
              protein_contains_DBD = any(protein_contains_DBD)) # use any to include protein isoforms
  
  #label DBD overlaps > 2 "3 or more"
  Domain.overlaps$interpro.overlaps[Domain.overlaps$interpro.overlaps > 2] <- "3 or more"
  
  #for symbols that do not contain any IPR DBD, label as none in protein
  Domain.overlaps$interpro.overlaps[!Domain.overlaps$protein_contains_DBD] <- "no annotated DBD"
  
  # order factor
  Domain.overlaps$interpro.overlaps <- factor(Domain.overlaps$interpro.overlaps) %>%
    fct_relevel(., c("no annotated DBD", "0", "1", "2", "3 or more"))
  
  Domain.overlaps <- Domain.overlaps %>%
    arrange(interpro.overlaps)
  

y <- ggplot(Domain.overlaps, aes(y="count", fill=interpro.overlaps)) +
  geom_bar() +
  theme_bw() + 
  ylab("") +
  xlab("number of proteins") +
  ggtitle(paste0("TF protein hits: ", nrow(Domain.overlaps))) +
  coord_flip() +
  scale_fill_manual("number of peptide overlaps", 
                    values = c("no annotated DBD" = "dodgerblue2",
                               "0" = "grey",
                               "1" = "grey44",
                               "2" = "black",
                               "3 or more" = "orange")) +
  theme(axis.text.x=element_blank(),
        text = element_text(size=10),
        axis.ticks.x = element_blank())
return(y)
})

p1 <- ggarrange(plotlist = DBD_plots, ncol = 1)

annotate_figure(p1, top = textGrob("RBR-ID hit overlap with Interpro DNA-binding Domains", gp = gpar(col = "black", fontsize = 20)))
```

## Fig4 volcano plots
```{r volcano_prep}
#load data
peplist <- readRDS(file.path(wd, "rds", "BR09_11_anno.IPR.wh.prot_rbd.quant.rds"))[run_index]

# RNA binding domain ids
RRM="IPR000504"
KH="IPR004087"
dsRBD="IPR014720"
ploop="IPR027417"
RBDs<- paste(RRM,KH,dsRBD, sep = "|")

Volcano_plots <- imap(peplist, function(rbrid, dataset) {
  trim_name <- gsub(x = dataset, pattern = "_.*", "")
  FDR = T
  if (dataset == "mESC" ) {
    FDR = F
  }
  
      #filter peptides for proteins with at least 3 peptides
    df <- rbrid %>%
      filter(peptides_detected > 2)
    
    # do not use FDR for mESC dataset
    if (FDR) {
       df <- df %>%
      mutate(log10_pval = -log10(padj))
      ylab <- "-log10 adj. p-value"
      xlimits <- c(3,3)
    } else {
      df <- df %>%
        mutate(log10_pval = -log10(pval))
      ylab <- "-log10 p-value"
      xlimits <- c(-5,5)
    }
  #initialize annotation
  df$Domain <- "all other peptides"
  
  #plot volcano plot for RBDs, ploop, and TFs
  index <- c(RBDs= "RBD",
             ploop="P-Loop",
             TFs="TF peptide")
  
  subplots <- map(index, function(subject){
  
  if (subject == "RBD") {
    df$Domain[grepl(RBDs, df$interpro_peptide)] <- "RBD"
    color = "red"
    
  } else if (subject == "P-Loop") {
    df$Domain[grepl(ploop, df$interpro_peptide)] <- "P-Loop"
    color = "blue"
    
  } else if (subject == "TF peptide") {
    TF_ind <- which(df$whitehead_TF != "")
    df$Domain[TF_ind] <- "TF peptide"
    color = "red"
  }
    df$Domain <- fct_relevel(df$Domain, "all other peptides") #reorder levels
    
    my_colors <- c("grey", color)
    names(my_colors) <- levels(df$Domain)
    g <- ggplot(df %>% arrange(Domain),
              aes(x = log2fold,
                  y = log10_pval,
                  col = Domain)) +
    theme_classic() +
    geom_point(alpha = 0.1, size =4) +
    scale_color_manual("",
                       values = my_colors,
                       breaks = subject) +
    xlab("Log2 fold change (+/- 4sU)") +
    ylab(ylab) +
    geom_hline(yintercept = -log10(0.05), linetype = 2, size = 0.4) +
    geom_vline(xintercept = 0, linetype = 2, size = 0.4) +
    xlim(-5, 5) + 
    ylim(0,7) +
     theme(text = element_text(size=10),
          legend.position = "top") +
    guides(color=guide_legend(override.aes=list(alpha=1))) #make legend color opaque
  
  z <- ggMarginal(g,type = "density",groupColour = T, margins = "x",
                    geom_vline(xintercept = 0, linetype = 2, size = 0.4))
    #add vertical dashed line to gtable object with density plot
    vline <- ggplot() +
      geom_vline(xintercept = 0, linetype = 2, size = 0.4) + #create dashed line
      theme_void() 
      vgrob <- ggplotGrob(vline) #convert to grob
      #use gtable_add_grob to add vertical line grob to object, plot underneath with z
      z$grobs[[20]] <- gtable_add_grob(z$grobs[[20]], vgrob, t=1, l=1, z = -Inf) 
      
      return(z)})
  
  return(subplots)
  })

p1 <- ggarrange(plotlist = Volcano_plots[[1]], nrow = 1)
p1
```

## Fig 5 rank plot 

```{r Rank Plot, eval = T}
peplist <- readRDS(file.path(wd, "rds", "BR09_11_anno.IPR.wh.prot_rbd.quant.rds"))[run_index]

rankplots <- future_imap(peplist, function(rbrid, dataset) {
  
  # make a temp copy to modify and fill missing symbols with uniprot IDs  
  rbrid.temp <- rbrid[rbrid$peptides_detected > 2, ]
  rbrid.temp$symbol[rbrid.temp$symbol==""] <- rbrid.temp$uniprotID[rbrid.temp$symbol==""]

  # generate protein-level RBR-ID score list
  red.flat <- rbrid.temp %>%
    group_by(symbol) %>%
    arrange(-score) %>%
    slice_head(n = 1)  %>% # keep the max RBR-ID per each protein
    ungroup() %>%
    arrange(score) %>%# Resort based on RBR-ID score %>%
  mutate(type  = factor(case_when(whitehead_TF != "" ~ "TFs",
                   TRUE ~ "All protein"), levels = c("All protein", "TFs")))
  red.flat$rank <- 1:nrow(red.flat) # assign rank
  
# ranked plot
p <- ggplot(red.flat %>%
              mutate(type = "All protein"), aes(x = rank, y = score)) +
  geom_point(size = 3, aes(col = type), show.legend = F) +
  geom_point(data = red.flat %>%
               filter(type == "TFs") %>%
               arrange(type),
             mapping = aes(col = type), size = 7, alpha = 0.1) +
  scale_color_manual("", labels = c("All protein", "TFs"),
                     values = c("grey", "navy")) +
  guides(colour = guide_legend(override.aes = list(alpha = 0.5))) + # override alpha for legend
  theme_bw() +
  ylab("RBR-ID score") +
  xlab("Rank") +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank()) +
  ggtitle(paste0("Ranked plot of max RBR-ID score per protein")) +
  theme(plot.title = element_text(hjust = 0.5)) +
  theme(legend.background = element_blank(),
        legend.box.background = element_rect(colour = "black"),
        text = element_text(size=10),
        legend.title = element_blank(),
        panel.border = element_rect(color = "black", fill = NA))

  if(dataset == "mESC") {
    p <- p + 
      scale_y_continuous(limits = c(-10, 120), breaks = base::seq(0, 100, 20))
  }
  

return(p)
})

p1 <- ggarrange(plotlist = rankplots[2], nrow = 1)
```

### Fig 6: CDF of TF RBR-ID scores

```{r CDF, eval = evalFlag}
# Prepare CDF data frames by normalizing their length
peplist <- readRDS(file.path(wd, "rds", "BR09_11_anno.IPR.wh.prot_rbd.quant.rds"))[run_index]

cdfplots <- future_imap(peplist, function(rbrid, dataset) {
  
  # make a temp copy to modify and fill mising symbols with uniprot IDs  
  rbrid.temp <- rbrid[rbrid$peptides_detected > 2, ]
  rbrid.temp$symbol[rbrid.temp$symbol==""] <-
    rbrid.temp$uniprotID[rbrid.temp$symbol==""]

  # generate protein-level RBR-ID score list
  red.flat <- rbrid.temp %>%
    group_by(symbol) %>%
    arrange(-score) %>%
    slice_head(n = 1)  %>% # keep the max RBR-ID per each protein
    ungroup() %>%
    arrange(score) %>%# Resort based on RBR-ID score %>%
  mutate(type  = factor(case_when(whitehead_TF != "" ~ "TFs",
                   TRUE ~ "All protein"), levels = c("All protein", "TFs")))
  red.flat$rank <- 1:nrow(red.flat) # assign rank

#sort score by ascending order
red.flat <- red.flat %>% 
  arrange(score) %>%
  mutate(fraction = 1:length(score)/length(score))

TFdata <-  red.flat %>%
              filter(type == "TFs") %>%
              mutate(fraction = 1:length(score)/length(score))

g <- ggplot(red.flat, aes(x = score, y = fraction)) +
  geom_line(data = red.flat %>%
              mutate(type = "All Proteins"),
            aes(col = type)) +
  geom_line(data = TFdata, aes(col = type), size = 1.3) +
  theme_classic() +
  ylab("Fraction of set") +
  xlab("RBR-ID score") +
  ggtitle("Ranked plot of max RBR-ID score per protein")+
  scale_color_manual(values = c("grey", "blue")) +
  scale_y_continuous(limits = c(0, 1), breaks = base::seq(0,1,0.2)) +
  coord_cartesian(xlim =c(-1,floor(TFdata$score[which(TFdata$fraction > 0.97)[1]]))) +
  theme(legend.background = element_blank(),
        legend.box.background = element_rect(colour = "black"),
        text = element_text(size=10),
        legend.title = element_blank(),
        panel.border = element_rect(color = "black", fill = NA))

 if(dataset == "mESC") {
    # g <- g + 
    #   scale_x_continuous(limits = c(-1, 17), breaks = base::seq(0, 15, 5))
 }

  if(dataset == "HepG2") {
    g <- g + 
      scale_x_continuous(limits = c(-2, 6), breaks = base::seq(-1, 5, 1))
 }

return(g)})

ggarrange(plotlist = cdfplots, nrow = 2)

```


## Arrange Figures
```{r arrange}
purrr::map(run_index, function(experiment) {

  #extract plots
  master <- list(volcano = Volcano_plots,
                 venn = venn_plots,
                 dbd = DBD_plots,
                 rank = rankplots,
                 cdf = cdfplots)
  subset <- map(master, experiment) #extract graph for each experiment
  
# pdf(file.path(wd, "figures", paste0("BR09_08_", experiment, "_RBRID.pdf")),
#     width = 8.5,
#     height = 11,
#     title = paste0("BR09_08_", experiment, "_RBRID"))
grid.arrange(grobs = c(subset$volcano, subset[2:5]),
             layout_matrix = matrix(c(1,1,2,2,3,3,
                                      4,4,4,5,5,5,
                                      6,6,6,7,7,7),
                                    ncol = 6,
                                    nrow = 3,
                                    byrow = T),
             widths = c(1,1,1,1,1,1),
             heights = c(3,3,3))
# dev.off()
})
```

# Output table for collaborators
```{r output_table, eval = evalFlag}
# run_index <- "HepG2"

peplist <- readRDS(file.path(wd, "rds", "BR09_02_anno.IPR.wh.prot_rbd.quant.rds"))[run_index]

imap(peplist, function(rbrid, dataset) {
  species <- Whatspecies(dataset)
  
outputCols <- c("uniprotID",
"symbol",
"whitehead_TF",
"synonyms",
"name",
"sequence",
"start",
"end",
"interpro_peptide",
"interpro_protein",
"interpro_DBD",
"peptides_detected",
"test_used",
"pval",
"padj",
"logFold",
"score")
  
  if (species == "mouse") {
    outputCols <- outputCols[outputCols!= "padj"]
  }
  
rbrid <- rbrid %>%as
  arrange(-score) %>%
  filter(!is.na(whitehead_TF))
# Select columns that they need and give them easier to interpret names

out <- rbrid %>% select(all_of(outputCols))
                        

# Save to TSV
write.table(out, file.path(wd, paste0("output/220519.TF.DBD.", dataset, ".table.tsv")), quote = F, row.names = F, sep = "\t")

return(NULL)
})
```